Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words

### 2020-08-06 paper/supplementary_material.Rmd
add rmd paper

plot_cg <- ggplot() +
  geom_hline(yintercept = 1/2, lty=2, size = 1)+
  geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), size = .025)+
  geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
  labs(x="Age",y="Proportion object new to speaker chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)

@@

```{r figa1, include = T, cache=T,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}

@@

```{r figa2, include = T, cache=T,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}

>>>>

plot_cg <- ggplot() +
  geom_hline(yintercept = 1/2, lty=2, size = 1)+
  geom_jitter(data = plot_cg_data,aes(x = age_num, y= correct), width = .00, height = .01, alpha = .5)+
  geom_line(data = plot_cg_samples, aes(x = age+min(prior_data$age_num), y = y, group = sample), alpha = .05)+
  geom_line(data = plot_cg_map, aes(x =age+min(prior_data$age_num), y = y), size = 1)+
  labs(x="Age",y="Proportion object new to speaker chosen")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)

@@

```{r figa1, include = T, cache=F,  fig.cap = "Posterior distribution of intercept term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}

@@

```{r figa2, include = T, cache=F,  fig.cap = "Posterior distribution of slope term for semantic knowledge for each object by model.", fig.width=12, fig.height = 6}
